\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-13 latex/article.tex
Småopdateringer af artikel

\newcommand{\hl}[1]{\textcolor{magenta}{#1}}
\newcommand{\R}{\proglang{R}\xspace}

@@

%% almost as usual
\author{Anne Helby Petersen\\Biostatistics\\Department of Public
  Health\\University of Copenhagen \And Claus Thorn Ekstr\o m\\Biostatistics\\Department of Public
  Health\\University of Copenhagen}
\title{\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}}

@@

\section{Introduction}
Statisticians and data analysts spend a large portion of their time on
data cleaning and on data wrangling. Packages such as
\pkg{data.table}, and \pkg{plyr} have made data wrangling a lot easier in
\proglang{R}, but there are only a few options available for automated data
cleaning.

@@

In \pkg{cleanR} the \code{clean} function is the primary workhorse and it
should be the primary entry point for data cleaning.

@@

\section{The structure of cleanR} \label{sec:internals}

@@

\section{To-dos in the code}
\hl{ ...  introduced by discrepancy between what I say we have done and what we have actually done:
\begin{itemize}
\item summaryFunction stuff:
	\begin{itemize}
		\item Make constructor function
		\item Make allSummaryFunctions()
		\item Change class of all summary (and description) functions into summaryFunction (possibly letting description functions be a subclass?)
		\item Maybe: Make clean check if summary functions are really summaryFunctions?
	\end{itemize}
\item visualFunction stuff:
	\begin{itemize}
		\item Make constructor function
		\item Make allVisualFunctions()
		\item Change class of all visual functions into visualFunction
		\item Maybe: Make clean check if visual functions are really visual functions?
	\end{itemize}
\item checkFunction stuff:
	\begin{itemize}
		\item Make allCheckFunctions()
		\item Work on messageGenerator() to make it better suited for being an exported function + export it
		\item Make allVisual()
	\end{itemize}
\end{itemize}
}

>>>>

\newcommand{\hl}[1]{\textcolor{magenta}{#1}}

%Virker ikke:
%\newcommand{\R}{\proglang{R}\xspace}

\newcommand{\R}[1]{\code{#1}}

@@

%% almost as usual
\author{Anne H. Petersen\\Biostatistics\\Department of Public
  Health\\University of Copenhagen \And Claus Thorn Ekstr\o m\\Biostatistics\\Department of Public
  Health\\University of Copenhagen}
\title{\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}}

@@

\section{Introduction}
Statisticians and data analysts spend a large portion of their time on
data cleaning and on data wrangling. Packages such as
\pkg{data.table}, and \pkg{plyr} have made data wrangling a lot easier in
\proglang{R}, but there are only a few options available for automated data
cleaning. \hl{Hov! Er det ikke et job for autocleanR?}

@@

\begin{table}
\begin{tabular}{p{0.2\linewidth}p{0.5\linewidth}p{0.2\linewidth}}
Argument & Description & Default value \\
\hline
\R{output} & Type of output file to be produced (html, pdf or no file) & \R{"pdf"} \\
\R{ordering} & Ordering of the variables in the data summary & \R{"asIs"} \\
\R{onlyProblematic} & Should only variables flagged as problematic be included in the output? & \R{FALSE} \\
\R{maxProbVals} & Maximum number of problematic values to print, if any are found in data checks & \R{Inf} \\
\R{maxDecimals} & Maximum number of decimals to print for numeric problematic values & \R{2}
\end{tabular}
\caption{A selection of commonly used arguments of \R{clean()}.}
\label{table.cleanFormals}
\end{table}

In \pkg{cleanR} the \code{clean} function is the primary workhorse and knowledge of nothing more than this function is required to produce data cleaning outputs in \pkg{cleanR}. The data cleaning output itself is an overview document, intended for reading by humans, in either pdf or html format.

@@

\section{Behind the scenes} \label{sec:internals}

@@

\section{To-dos in the code}
\hl{ ...  introduced by discrepancy between what I say we have done and what we have actually done:
(nothing right now)
}
